Spin canonical divisors of log stacky curves

### 2015-06-29 stacky_write_up/spin_cring.tex
minor intro edits

Let $X$ be a smooth algebraic curve over $k$ of genus $g$. It is
well known that the canonical sheaf $\Omega _X,$ with associated canonical divisor $K_X$
 determines the {\bf canonical map } $\pi:X \rightarrow \BP_k^{g - 1}$.
Then, the {\bf canonical ring} is defined to be
\begin{align*}
	R(X,K_X) = \bigoplus_{n \geq 0} H^0(X,nK_X),
\end{align*}

@@

The remainder of the paper will be primarily devoted to proving
Theorem ~\ref{thm:main}. The idea of the
proof will be to induct on the order and number of stacky points. To this end, we first review important background in
Section ~\ref{sec:background}. Then, we develop various inductive
tools in Section ~\ref{sec:induction}. In Sections ~\ref{sec:g_high},
~\ref{sec:g_1}, and ~\ref{sec:g_0}, we prove Theorem
~\ref{thm:main} in the high genus, genus
one, and genus zero cases respectively. Finally, in Section
~\ref{sec:further-questions}, we pose several questions for future
research.

\todo{incorporate some chunk on O'Dorney somewhere in intro, below is previously written stuff}
In \cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a (not-necessarily effective) \todo{Can we remove this parenthetical? I don't see why the reader would assume effective.} divisor $D=\frac{\alpha_1}{\beta_1}P_1+\frac{\alpha_2}{\beta_2}P_2$ of $\BP_k^1$ \todo{This comes up a lot, but instead of saying $D$ is a divisor of $X$, I'd prefer to say $D \in \di X$ to be more precise. Of course, this is minor, and it's fine to keep it this way.} consisting of at most 2 points in its support, \todo{It might be clearer to say $\# \Supp(D) \leq 2.$} to show it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$. \todo{Can you break the previous sentence into two sentences?} He \todo{Probably better not to say he, maybe give a theorem number where he does this?} further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points. \todo{This sentence seems very imprecise to me, and I wouldn't understand it if I hadn't read Evan's paper. Can you state this more precisely, or possibly just remove it.}

>>>>

Let $X$ be a smooth algebraic curve over $k$ of genus $g$. It is
well known that the canonical sheaf $\Omega _X,$ with associated canonical divisor $K_X$
 determines the {\bf canonical map } $\pi:X \rightarrow \BP_k^{g - 1}$.
Then, the {\bf canonical ring} is defined to be
\begin{align*}
	R(X,K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
\end{align*}

@@

The main theorem of this paper provides the following application
to modular forms when combined with a result from Voight and
Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky}.

\begin{cor}
\label{cor:main-mod-forms}
There exists a log half-canonical divisor $\halfcan$ on $\sx$ such
that we have a graded isomorphism of $\BC$-algebras
\[
	\bigoplus_{k = 0}^{\infty} M_k(\Gamma) \cong R(\sx (\Gamma), 
\Delta, \halfcan)
\]

\noindent
Let $\sigma = (g; e_1, \ldots, e_r; \delta)$ be the signature
of $\sx$. Then $\bigoplus_{k = 0}^{\infty} M_k(\Gamma)$ is
generated as a $\BC$-algebra by elements of degree at most $e = \max
(5, e_1, \ldots, e_r).$ If the genus $g \geq 2,$ and $\Delta = 0$
then $R(\sx,\Delta, \halfcan)$ has relations generated in degrees
up to $\max(11, 2e_1, \ldots, 2e_r)$. Otherwise, $R(\sx, \Delta,
\halfcan)$ has relations generated in degrees up to $\max(10, 2e_1,
\ldots, 2e_r),$ so long as $\sigma$ does not lie in a finite list
of exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}
for signatures with $g = 1$ and Table ~\ref{table:g-0-exceptional}
for signatures with $g = 0$.
\end{cor}

The remainder of the paper will be primarily devoted to proving
Theorem ~\ref{thm:main}. The idea of the
proof will be to induct on the stabilizer order of and number of stacky points. To this end, we first review important background in
Section ~\ref{sec:background}. Then, we develop various inductive
tools in Section ~\ref{sec:induction}. In Sections ~\ref{sec:g_high},
~\ref{sec:g_1}, and ~\ref{sec:g_0}, we prove Theorem
~\ref{thm:main} in the high genus, genus
one, and genus zero cases respectively. Finally, in Section
~\ref{sec:further-questions}, we pose several questions for future
research.

\todo{incorporate some chunk on O'Dorney somewhere in intro, below is previously written stuff}
In \cite{dorney:canonical}, O'Dorney uses best lower approximations to provide a minimal presentation for the canonical ring of a divisor $D = \frac{\alpha_1}{\beta_1}P_1 + \frac{\alpha_2}{\beta_2}P_2$ of $\BP_k^1$ \todo{This comes up a lot, but instead of saying $D$ is a divisor of $X$, I'd prefer to say $D \in \di X$ to be more precise. Of course, this is minor, and it's fine to keep it this way.} with at most 2 points in its support, \todo{It might be clearer to say $\# \Supp(D) \leq 2.$} to show it is generated in degree $e=\max{\beta_1,\beta_2}$ with relations generated in degrees at most $2e$. \todo{Can you break the previous sentence into two sentences?} He \todo{Probably better not to say he, maybe give a theorem number where he does this?} further extends the result to more points, but only bounds the degree of minimal generation by a value on the order the least common multiple of the denominators of fractional points. \todo{This sentence seems very imprecise to me, and I wouldn't understand it if I hadn't read Evan's paper. Can you state this more precisely, or possibly just remove it.}
